---
title: "DiabetesPrediction"
author: "Balaji VR"
date: "1/15/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Diabetes Prediction based on different Exercise(Physical Activity) performed
####Center of Disease Control and Prevention(CDC) is an organization working 24/7 to save protect USA from Health and Safety threats, both Foreign and Domestic. CDC has different branches, within which BRFSS and Diabetes are different branch which possess the Survey Data of the people. 
##### With the available data, We want to predict the type 2 diabetes 
##### Prediabetes means a person’s blood glucose (sugar) level is higher than normal, but not high enough yet for a diagnosis of type 2 diabetes. If left untreated, prediabetes can progress into type 2 diabetes. And if 1 in 3 American adults has prediabetes, that means it could be you, your favorite sibling, or your other sibling. Or you, your barber, your barber’s barber. Or you—well, you get the picture. It’s time to take the risk test to know where you stand.
```{r}

#Setting the Capstone Project working directory
setwd("/Users/balajivr/Desktop/BABI/Capstone/Health")
cat("Working Directory:", getwd(),"\n")

```

```{r}
if (!require("foreign")) install.packages("foreign")
library("foreign")

#XPT is SAS format file which is available from CDC BRFSS. We need to use foreign package to export and converted to dataset
#mydata <- read.xport("LLCP2017.XPT")
#summary(mydata)
```

```{r warning=FALSE, paged.print=FALSE}
#library Dataexplorer needed to for EDA analysis
library(DataExplorer)

#Processed Dataset with all relevant needed for Diabetes Prediction
prData <- read.csv("new_cdc_data.csv", header = TRUE)
summary(prData)

#Missing data analysis
plot_missing(prData)
```

```{r message=TRUE, warning=FALSE, paged.print=FALSE}
plot_correlation(prData, type = "continuous")
create_report(prData)
```

###References
####1. Centers for Disease Control and Prevention. Methodologic changes in the Behavioral Risk Factor Surveillance System in 2011 and potential effects on prevalence estimates [article online]. Available here. 2013.

####2. Klein RJ, Schoeborn CA. Age adjustment using the 2000 projected US population. Healthy People Statistical Notes. 2001;20:1-10.

####3. Centers for Disease Control and Prevention. National Diabetes Statistics Report, 2017. Atlanta, GA: US Department of Health and Human Services; 2017.

####4. Centers for Disease Control and Prevention. Division of Diabetes Translation. United States Diabetes Surveillance System: Frequently Asked Questions. Available here.

####5. Centers for Disease Control and Prevention. Behavioral Risk Factor Surveillance System. Overview: BRFSS 2013 [article online]. Available here.2014.

####6. Li YF, Geiss LS, Burrows NR, Rolka DB, Albright A. Awareness of prediabetes - United States, 2005-2010. MMWR Morb Mortal Wkly Rep. 2013;62(11):209-212

####7. Saydah SH, Geiss LS, Tierney E, Benjamin SM, Engelgau M, Brancati F. Review of the performance of methods to identify diabetes cases among vital statistics, administrative, and survey data. Annals Epidemiol. 2004;14(7):507-516.

####8. MacLennan PA, McGwin G Jr, Searcey K, Owsley C. Medical record validation of self-reported eye diseases and eye care utilization among older adults. Curr Eye Res. 2013;38(1):1-8.

####9. Toobert DJ, Hampson SE, Glasgow RE. The summary of diabetes self-care activities measure: results from 7 studies and a revised scale. Diabetes Care. 2000;23(7):943-950.

####10. Harwell TS, Moore K, Madison M, Powell-Taylor D, Lundgren P, Smilie JG, Acton KJ, Helgerson SD, Gohdes D. Comparing self-reported measures of diabetes care with similar measures from a chart audit in a well-defined population. Am J Med Qual. 2001;16(1):3-8.

####11. Fowles JB, Rosheim K, Fowler EJ, Craft C, Arrichiello L. The validity of self-reported diabetes quality of care measures. Int J Qual Health Care. 1999;11(5):407-412.

####12. Hutchison BG. Measurement of influenza vaccination status of the elderly by mailed questionnaire: response rate, validity and cost. Can J Public Health. 1989;80(4):271-275.

####13. MacDonald R, Baken L, Nelson A, Nichol KL. Validation of self-report of influenza and pneumococcal vaccination status in elderly outpatients. Am J Prev Med. 1999;16(3):173-177.

####14. United States Renal Data System. 2017 USRDS Annual Data report: Epidemiology of Kidney Disease in the United States. National Institutes of Health, National Institute of Diabetes and Digestive and Kidney Diseases, Bethesda, MD, 2017. Available here.